Hydra Battles and Cie

### 2020-11-16 doc/chapter-powers.tex
minor changes

\begin{Coqsrc}
Fixpoint power (x:A)(n:nat) : A :=
  match n with 0%nat => 1
             | S p =>   x * x ^ p
  end
where "x ^ n" := (power x n).

@@

The number of multiplications needed to compute $x^n$ via this function is linear with respect to $n$. Despite this lack of efficiency, and thanks to its simplicity, we keep it as a specification for more efficient and complex exponentiation algorithms.
A function will be considered a \emph{correct} exponentiation function if we can prove it is extensionally equivalent to \texttt{power}.

>>>>

\begin{Coqsrc}
Fixpoint power (x:A)(n:nat) : A :=
  match n with 
   | 0%nat => 1
   | S p =>   x * x ^ p
  end
where "x ^ n" := (power x n).

@@

An application of this function for  computing $x^n$ needs $n$ multiplications.
 Despite this lack of efficiency, and thanks to its simplicity, we keep it as a specification for more efficient and complex exponentiation algorithms.
A function will be considered a \emph{correct} exponentiation function if we can prove it is extensionally equivalent to \texttt{power}.
